### 2019-12-20 article.tex
typo in calculations fixed, statistics added to result tables

\begin{figure*}
	\includegraphics[width=\linewidth]{images/3dCnn}
	\caption{3D CNN demonstration (kernel size = 3$\times$3$\times$3).}
	\label{fig:CnnSample}
\end{figure*}

@@

\begin{table}
	\caption{Average accuracies for different tests}
	\begin{tabular}{| c | c | c| }
		\hline
		$j$ & $\overline{C_{i,t}}\;(\%)$ & $\overline{C_i}\;(\%)$ \\ 
		test no. & mean time-slice accuracy & mean accuracy \\ \hline
		1 & 100 & 100 \\
		2 & 97.90 & 100 \\
		3 & 74.83 & 83.33 \\
		4 & 96.30 & 100 \\
		5 & 97.14 & 100 \\
		6 & 100 & 100 \\
		7 & 98.65 & 100 \\
		8 & 78.87 & 83.33 \\ \hline
		Average & $\mathbf{C_t} = $ 92.96 & $\mathbf{C} = $ 95.83 \\
		\hline
	\end{tabular}
\label{table:averageAccuracies}
\end{table}

As we can see, the proposed method has shown huge success in the task of Parkinson's disease diagnosis in an affordable time. Also, the fascinating point about the experiments is the average mean time-slice accuracy which is around $92.96\%$. Accordingly, it means the model is able to judge only by a single time-slice of the brain while the prediction is acceptably accurate. We mostly care about the average mean accuracy, which is the average accuracy of the disease diagnosis task and as long as the whole process can predict someone's health situation precisely, we can ignore the time-slice based results. So, we should mostly focus on average mean accuracy and use that to compare the proposed method to other models.

\begin{table}
	\caption{Test results for experiment 1. HC stands for Health Control while P means Parkinson's disease}
	\resizebox{\linewidth}{!}{%
		\begin{tabular}{ | c | c | c | c | c | c | c | c | }
			\hline
			patient & $Y_i$ & $N_{hc}$ & $N_p$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
			CTL04 & HC & 198 &  0  & 100 & 1 & HC & 100 \\
			CTL05 & HC & 198 &  0  & 100 & 1 & HC & 100 \\
			CTL02 & HC & 198 &  0  & 100 & 1 & HC & 100 \\
			ODP04 & P   &  0  & 198 & 100 & 0 &  P  & 100 \\
			ODP05 & P   &  0  & 198 & 100 & 0 &  P  & 100 \\
			ODP02 & P   &  0  & 198 & 100 & 0 &  P  & 100 \\ \hline
			\multicolumn{4}{|r|}{\tiny{Mean time-slice accuracy} $\overline{C_{i,t}}$} & 100 &
			\multicolumn{2}{|r|}{\tiny{Mean accuracy} $\overline{C_{i}}$} & 100 \\
			\hline
		\end{tabular}
	}
	\label{table:tests_1}
\end{table}
\begin{figure}
	\includegraphics[width=\linewidth]{images/tests_1}
	\caption{Experiment 1. Accuracy and loss of network for training and validation data. Accuracy is based on validation data and loss diagram contains train data loss in blue and validation loss in orange.}
	\label{fig:tests_1}
\end{figure}

\begin{table}
	\caption{Test results for experiment 2.}
	\resizebox{\linewidth}{!}{%
		\begin{tabular}{ | c | c | c | c | c | c | c | c | }
			\hline
			patient & $Y_i$ & $N_{hc}$ & $N_p$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
			CTL08 & HC & 191 &  7  & 96.46 & 0.9646 & HC & 100 \\
			CTL12 & HC & 195 &  3  & 98.48 & 0.9848 & HC & 100 \\
			CTL01 & HC & 198 &  0  & 100 & 1 & HC & 100 \\
			ODP08 & P   &  1  & 197 & 99.49 & 0.0050 &  P  & 100 \\
			ODP12 & P   &  2  & 196 & 98.99 & 0.0101 &  P  & 100 \\
			ODP01 & P   &  12  & 186 & 93.94 & 0.0606 &  P  & 100 \\ \hline
			\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 97.90 &
			\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 100 \\
			\hline
		\end{tabular}
	}
	\label{table:tests_2}
\end{table}
\begin{figure}
	\includegraphics[width=\linewidth]{images/tests_2}
	\caption{Experiment 2. Accuracy and loss of network for training and validation data.}
	\label{fig:tests_2}
\end{figure}

\begin{table}
\caption{Test results for experiment 3.}
\resizebox{\linewidth}{!}{%
	\begin{tabular}{ | c | c | c | c | c | c | c | c | }
		\hline
		patient & $Y_i$ & $N_{hc}$ & $N_p$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
		CTL03 & HC & 198 &  0   &   100   &     1      & HC & 100 \\
		CTL13 & HC & 198 &  0   &   100   &     1      & HC & 100 \\
		CTL14 & HC & 198 &  0   &   100   &     1      & HC & 100 \\
		ODP03 & P  &  53  & 145 & 73.23 & 0.2677 &  P  & 100 \\
		ODP13 & P  & 198 &   0   &     0    &      1      & HC  & 0 \\
		ODP14 & P  & 48  &  150 & 75.76  & 0.2424 &  P  & 100 \\ \hline
		\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 74.83 &
		\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 83.33 \\
		\hline
	\end{tabular}
}
\label{table:tests_3}
\end{table}
\begin{figure}
\includegraphics[width=\linewidth]{images/tests_3}
\caption{Experiment 3. Accuracy and loss of network for training and validation data.}
\label{fig:tests_3}
\end{figure}

\begin{table}
\caption{Test results for experiment 4.}
\resizebox{\linewidth}{!}{%
	\begin{tabular}{ | c | c | c | c | c | c | c | c | }
		\hline
		patient & $Y_i$ & $N_{hc}$ & $N_p$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
		CTL12 & HC & 185 & 13  & 93.43 & 0.9343 & HC & 100 \\
		CTL06 & HC & 197 &  1   & 99.49 & 0.9949 & HC & 100 \\
		CTL11 & HC & 170 & 28  & 85.86 & 0.8586 & HC & 100 \\
		ODP12 & P  &   0   & 198 &  100   &      0     &  P  & 100 \\
		ODP06 & P  &   0   & 198 &  100   &      0     &  P  & 100 \\
		ODP11 & P  &   2   & 196 & 98.99 & 0.0101  &  P  & 100 \\ \hline
		\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 96.30 &
		\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 100  \\
		\hline
	\end{tabular}
}
\label{table:tests_4}
\end{table}
\begin{figure}
\includegraphics[width=\linewidth]{images/tests_4}
\caption{Experiment 4. Accuracy and loss of network for training and validation data.}
\label{fig:tests_4}
\end{figure}

\begin{table}
\caption{Test results for experiment 5.}
\resizebox{\linewidth}{!}{%
	\begin{tabular}{ | c | c | c | c | c | c | c | c | }
		\hline
		patient & $Y_i$ & $N_{hc}$ & $N_p$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
		CTL15 & HC & 198 &   0   &  100  & 1 & HC & 100 \\
		CTL11 & HC & 198  &   0   &  100  & 1 & HC & 100 \\
		CTL07 & HC & 198 &   0   &  100  & 1 & HC & 100 \\
		ODP15 & P   &   0   & 198 &  100  & 0 &  P  & 100 \\
		ODP11 & P   &  34  &  164 &82.83& 0.1717 &  P  & 100 \\
		ODP07 & P  &   0   &  198 & 1 00  &0  &  P  & 100 \\ \hline
		\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 97.14 &
		\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 100 \\
		\hline
	\end{tabular}
}
\label{table:tests_5}
\end{table}
\begin{figure}
\includegraphics[width=\linewidth]{images/tests_5}
\caption{Experiment 5. Accuracy and loss of network for training and validation data.}
\label{fig:tests_5}
\end{figure}

\begin{table}
\caption{Test results for experiment 6.}
\resizebox{\linewidth}{!}{%
	\begin{tabular}{ | c | c | c | c | c | c | c | c | }
		\hline
		patient & $Y_i$ & $N_{hc}$ & $N_p$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
		CTL10 & HC & 198 &  0 & 100 & 1 & HC & 100 \\
		CTL03 & HC & 198 &  0 & 100 & 1 & HC & 100 \\
		CTL02 & HC & 198 &  0 & 100 & 1 & HC & 100 \\
		ODP10 & P  &  0  & 198 & 100 & 0 &  P  & 100 \\
		ODP03 & P  &  0  & 198 & 100 & 0 &  P  & 100 \\
		ODP02 & P  &  0  & 198 & 100 & 0 &  P  & 100 \\ \hline
		\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 100 &
		\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 100 \\
		\hline
	\end{tabular}
}
\label{table:tests_6}
\end{table}
\begin{figure}
\includegraphics[width=\linewidth]{images/tests_6}
\caption{Experiment 6. Accuracy and loss of network for training and validation data.}
\label{fig:tests_6}
\end{figure}

\begin{table}
\caption{Test results for experiment 7.}
\resizebox{\linewidth}{!}{%
	\begin{tabular}{ | c | c | c | c | c | c | c | c | }
		\hline
		patient & $Y_i$ & $N_{hc}$ & $N_p$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
		CTL05 & HC & 194 &  4   & 97.98 & 0.9798 & HC & 100 \\
		CTL04 & HC & 198 &  0   &   100  &      1     & HC & 100 \\
		CTL10 & HC & 186  &  12 & 93.94 & 0.9394 & HC & 100 \\
		ODP05 & P  &   0   & 198 &   100  &     0     &  P  & 100 \\
		ODP04 & P  &   0   & 198 &   100  &     0     &  P  & 100 \\
		ODP10 & P  &   0    & 198 &   100  &    0      &  P  & 100 \\ \hline
		\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 98.65 &
		\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 100 \\
		\hline
	\end{tabular}
}
\label{table:tests_7}
\end{table}
\begin{figure}
\includegraphics[width=\linewidth]{images/tests_7}
\caption{Experiment 7. Accuracy and loss of network for training and validation data.}
\label{fig:tests_7}
\end{figure}

\begin{table}
\caption{Test results for experiment 8.}
\resizebox{\linewidth}{!}{%
	\begin{tabular}{ | c | c | c | c | c | c | c | c | }
		\hline
		patient & $Y_i$ & $N_{hc}$ & $N_p$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
		CTL09 & HC & 25  & 173 & 12.63 &  0.1263 &  P  & 0 \\
		CTL12 & HC & 122 &  76  & 61.62 & 0.6162 & HC & 100 \\
		CTL06 & HC & 198 &   0  &  100   &    1       & HC & 100 \\
		ODP09 & P  &   0   & 198 &  100   &    0       &  P  & 100 \\
		ODP12 &  P  &   2   & 196 & 98.99 & 0.0101 &  P  & 100 \\
		ODP06 & P  &   0   & 198 &  100   &    0       &  P  & 100 \\ \hline
		\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 78.87 &
		\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 83.33 \\
		\hline
	\end{tabular}
}
\label{table:tests_8}
\end{table}
\begin{figure}
\includegraphics[width=\linewidth]{images/tests_8}
\caption{Experiment 8. Accuracy and loss of network for training and validation data.}
\label{fig:tests_8}
\end{figure}

>>>>

\begin{figure*}
	\includegraphics[width=0.8\linewidth]{images/3dCnn}
	\caption{3D CNN demonstration (kernel size = 3$\times$3$\times$3).}
	\label{fig:CnnSample}
\end{figure*}

@@

\begin{table}
	\caption{Average accuracies for different tests}
	\begin{tabular}{| c | c | c| }
		\hline
		$j$ & $\overline{C_{i,t}}\;(\%)$ & $\overline{C_i}\;(\%)$ \\ 
		test no. & mean time-slice accuracy & mean accuracy \\ \hline
		1 & 100 & 100 \\
		2 & 97.90 & 100 \\
		3 & 74.83 & 83.33 \\
		4 & 96.30 & 100 \\
		5 & 97.14 & 100 \\
		6 & 100 & 100 \\
		7 & 98.65 & 100 \\
		8 & 85.35 & 100 \\ \hline
		Average & $\mathbf{C_t} = $ 93.77 & $\mathbf{C} = $ 97.92 \\
		\hline
	\end{tabular}
\label{table:averageAccuracies}
\end{table}

As we can see, the proposed method has shown huge success in the task of Parkinson's disease diagnosis in an affordable time. Also, the fascinating point about the experiments is the average mean time-slice accuracy, which is around $92.96\%$. Accordingly, it means the model is able to judge only by a single time-slice of the brain while the prediction is acceptably accurate. We mostly care about the average mean accuracy, which is the average accuracy of the disease diagnosis task and as long as the whole process can predict someone's health situation precisely, we can ignore the time-slice based results. So, we should mostly focus on average mean accuracy and use that to compare the proposed method to other models.

\begin{table}
	\caption{Test results for experiment 1. HC stands for Health Control while P means Parkinson's disease}
	\resizebox{\linewidth}{!}{%
		\begin{tabular}{ | c | c | c | c | c | c | c | c | }
			\hline
			patient & $Y_i$ & $N_{hc}$ & $N_p$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
			CTL04 & HC & 198 &  0  & 100 & 1 & HC & 100 \\
			CTL05 & HC & 198 &  0  & 100 & 1 & HC & 100 \\
			CTL02 & HC & 198 &  0  & 100 & 1 & HC & 100 \\
			ODP04 & P   &  0  & 198 & 100 & 0 &  P  & 100 \\
			ODP05 & P   &  0  & 198 & 100 & 0 &  P  & 100 \\
			ODP02 & P   &  0  & 198 & 100 & 0 &  P  & 100 \\ \hline
			\multicolumn{4}{|r|}{\tiny{Mean time-slice accuracy} $\overline{C_{i,t}}$} & 100 &
			\multicolumn{2}{|r|}{\tiny{Mean accuracy} $\overline{C_{i}}$} & 100 \\
			\hline \hline

			\multicolumn{2}{|r|}{True positive (TP)} & 
			\multicolumn{2}{c|}{ 3 } &
			\multicolumn{2}{|r|}{False positive (FP)} & 
			\multicolumn{2}{c|}{ 0 } \\ 
			\multicolumn{2}{|r|}{False negative (FN)} & 
			\multicolumn{2}{c|}{ 0 } &
			\multicolumn{2}{|r|}{True negative (TN)} & 
			\multicolumn{2}{c|}{ 3 }  \\
			\hline \hline

			\multicolumn{2}{|r|}{Time-slice TP} & 
			\multicolumn{2}{c|}{ 594 } &
			\multicolumn{2}{|r|}{Time-slice FP} & 
			\multicolumn{2}{c|}{ 0 } \\ 
			\multicolumn{2}{|r|}{Time-slice FN} & 
			\multicolumn{2}{c|}{ 0 } &
			\multicolumn{2}{|r|}{Time-slice TN} & 
			\multicolumn{2}{c|}{ 594 }  \\
			\hline \hline

			\multicolumn{2}{|r|}{Time-slice sensitivity} & 
			\multicolumn{2}{c|}{ 1 } &
			\multicolumn{2}{|r|}{Sensitivity} & 
			\multicolumn{2}{c|}{ 1 } \\

			\multicolumn{2}{|r|}{Time-slice specificity} & 
			\multicolumn{2}{c|}{ 1 } &
			\multicolumn{2}{|r|}{Specificity} & 
			\multicolumn{2}{c|}{ 1 } \\

			\multicolumn{2}{|r|}{Time-slice PPV} & 
			\multicolumn{2}{c|}{ 1 } &
			\multicolumn{2}{|r|}{PPV} & 
			\multicolumn{2}{c|}{ 1 } \\

			\multicolumn{2}{|r|}{Time-slice NPV} & 
			\multicolumn{2}{c|}{ 1 } &
			\multicolumn{2}{|r|}{NPV} & 
			\multicolumn{2}{c|}{ 1 } \\ \hline
		\end{tabular}
	}
	\label{table:tests_1}
\end{table}
\begin{figure}
	\includegraphics[width=\linewidth]{images/tests_1}
	\caption{Experiment 1. Accuracy and loss of network for training and validation data. Accuracy is based on validation data and loss diagram contains train data loss in blue and validation loss in orange.}
	\label{fig:tests_1}
\end{figure}

\begin{table}
	\caption{Test results for experiment 2.}
	\resizebox{\linewidth}{!}{%
		\begin{tabular}{ | c | c | c | c | c | c | c | c | }
			\hline
			patient & $Y_i$ & $N_{hc}$ & $N_p$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
			CTL08 & HC & 191 &  7  & 96.46 & 0.9646 & HC & 100 \\
			CTL12 & HC & 195 &  3  & 98.48 & 0.9848 & HC & 100 \\
			CTL01 & HC & 198 &  0  & 100 & 1 & HC & 100 \\
			ODP08 & P   &  1  & 197 & 99.49 & 0.0050 &  P  & 100 \\
			ODP12 & P   &  2  & 196 & 98.99 & 0.0101 &  P  & 100 \\
			ODP01 & P   &  12  & 186 & 93.94 & 0.0606 &  P  & 100 \\ \hline
			\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 97.90 &
			\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 100 \\
			\hline \hline

			\multicolumn{2}{|r|}{True positive (TP)} & 
			\multicolumn{2}{c|}{ 3 } &
			\multicolumn{2}{|r|}{False positive (FP)} & 
			\multicolumn{2}{c|}{ 0 } \\ 
			\multicolumn{2}{|r|}{False negative (FN)} & 
			\multicolumn{2}{c|}{ 0 } &
			\multicolumn{2}{|r|}{True negative (TN)} & 
			\multicolumn{2}{c|}{ 3 }  \\
			\hline \hline

			\multicolumn{2}{|r|}{Time-slice TP} & 
			\multicolumn{2}{c|}{ 584 } &
			\multicolumn{2}{|r|}{Time-slice FP} & 
			\multicolumn{2}{c|}{ 15 } \\ 
			\multicolumn{2}{|r|}{Time-slice FN} & 
			\multicolumn{2}{c|}{ 10 } &
			\multicolumn{2}{|r|}{Time-slice TN} & 
			\multicolumn{2}{c|}{ 579 }  \\
			\hline \hline

			\multicolumn{2}{|r|}{Time-slice sensitivity} & 
			\multicolumn{2}{c|}{ 0.983164983 } &
			\multicolumn{2}{|r|}{Sensitivity} & 
			\multicolumn{2}{c|}{ 1 } \\

			\multicolumn{2}{|r|}{Time-slice specificity} & 
			\multicolumn{2}{c|}{ 0.974747475 } &
			\multicolumn{2}{|r|}{Specificity} & 
			\multicolumn{2}{c|}{ 1 } \\

			\multicolumn{2}{|r|}{Time-slice PPV} & 
			\multicolumn{2}{c|}{ 0.974958264 } &
			\multicolumn{2}{|r|}{PPV} & 
			\multicolumn{2}{c|}{ 1 } \\

			\multicolumn{2}{|r|}{Time-slice NPV} & 
			\multicolumn{2}{c|}{ 0.983022071 } &
			\multicolumn{2}{|r|}{NPV} & 
			\multicolumn{2}{c|}{ 1 } \\ \hline
		\end{tabular}
	}
	\label{table:tests_2}
\end{table}
\begin{figure}
	\includegraphics[width=\linewidth]{images/tests_2}
	\caption{Experiment 2. Accuracy and loss of network for training and validation data.}
	\label{fig:tests_2}
\end{figure}

\begin{table}
\caption{Test results for experiment 3.}
\resizebox{\linewidth}{!}{%
	\begin{tabular}{ | c | c | c | c | c | c | c | c | }
		\hline
		patient & $Y_i$ & $N_{hc}$ & $N_p$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
		CTL03 & HC & 198 &  0   &   100   &     1      & HC & 100 \\
		CTL13 & HC & 198 &  0   &   100   &     1      & HC & 100 \\
		CTL14 & HC & 198 &  0   &   100   &     1      & HC & 100 \\
		ODP03 & P  &  53  & 145 & 73.23 & 0.2677 &  P  & 100 \\
		ODP13 & P  & 198 &   0   &     0    &      1      & HC  & 0 \\
		ODP14 & P  & 48  &  150 & 75.76  & 0.2424 &  P  & 100 \\ \hline
		\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 74.83 &
		\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 83.33 \\
		\hline \hline

		\multicolumn{2}{|r|}{True positive (TP)} & 
		\multicolumn{2}{c|}{ 3 } &
		\multicolumn{2}{|r|}{False positive (FP)} & 
		\multicolumn{2}{c|}{ 1 } \\ 
		\multicolumn{2}{|r|}{False negative (FN)} & 
		\multicolumn{2}{c|}{ 0 } &
		\multicolumn{2}{|r|}{True negative (TN)} & 
		\multicolumn{2}{c|}{ 2 }  \\
		\hline \hline

		\multicolumn{2}{|r|}{Time-slice TP} & 
		\multicolumn{2}{c|}{ 594 } &
		\multicolumn{2}{|r|}{Time-slice FP} & 
		\multicolumn{2}{c|}{ 299 } \\ 
		\multicolumn{2}{|r|}{Time-slice FN} & 
		\multicolumn{2}{c|}{ 0 } &
		\multicolumn{2}{|r|}{Time-slice TN} & 
		\multicolumn{2}{c|}{ 295 }  \\
		\hline \hline

		\multicolumn{2}{|r|}{Time-slice sensitivity} & 
		\multicolumn{2}{c|}{ 1 } &
		\multicolumn{2}{|r|}{Sensitivity} & 
		\multicolumn{2}{c|}{ 1 } \\

		\multicolumn{2}{|r|}{Time-slice specificity} & 
		\multicolumn{2}{c|}{ 0.496632997 } &
		\multicolumn{2}{|r|}{Specificity} & 
		\multicolumn{2}{c|}{ 0.666666667 } \\

		\multicolumn{2}{|r|}{Time-slice PPV} & 
		\multicolumn{2}{c|}{ 0.665173572 } &
		\multicolumn{2}{|r|}{PPV} & 
		\multicolumn{2}{c|}{ 0.75 } \\

		\multicolumn{2}{|r|}{Time-slice NPV} & 
		\multicolumn{2}{c|}{ 1 } &
		\multicolumn{2}{|r|}{NPV} & 
		\multicolumn{2}{c|}{ 1 } \\ \hline
	\end{tabular}
}
\label{table:tests_3}
\end{table}
\begin{figure}
\includegraphics[width=\linewidth]{images/tests_3}
\caption{Experiment 3. Accuracy and loss of network for training and validation data.}
\label{fig:tests_3}
\end{figure}

\begin{table}
\caption{Test results for experiment 4.}
\resizebox{\linewidth}{!}{%
	\begin{tabular}{ | c | c | c | c | c | c | c | c | }
		\hline
		patient & $Y_i$ & $N_{hc}$ & $N_p$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
		CTL12 & HC & 185 & 13  & 93.43 & 0.9343 & HC & 100 \\
		CTL06 & HC & 197 &  1   & 99.49 & 0.9949 & HC & 100 \\
		CTL11 & HC & 170 & 28  & 85.86 & 0.8586 & HC & 100 \\
		ODP12 & P  &   0   & 198 &  100   &      0     &  P  & 100 \\
		ODP06 & P  &   0   & 198 &  100   &      0     &  P  & 100 \\
		ODP11 & P  &   2   & 196 & 98.99 & 0.0101  &  P  & 100 \\ \hline
		\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 96.30 &
		\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 100  \\
		\hline \hline

		\multicolumn{2}{|r|}{True positive (TP)} & 
		\multicolumn{2}{c|}{ 3 } &
		\multicolumn{2}{|r|}{False positive (FP)} & 
		\multicolumn{2}{c|}{ 0 } \\ 
		\multicolumn{2}{|r|}{False negative (FN)} & 
		\multicolumn{2}{c|}{ 0 } &
		\multicolumn{2}{|r|}{True negative (TN)} & 
		\multicolumn{2}{c|}{ 3 }  \\
		\hline \hline

		\multicolumn{2}{|r|}{Time-slice TP} & 
		\multicolumn{2}{c|}{ 552 } &
		\multicolumn{2}{|r|}{Time-slice FP} & 
		\multicolumn{2}{c|}{ 2 } \\ 
		\multicolumn{2}{|r|}{Time-slice FN} & 
		\multicolumn{2}{c|}{ 42 } &
		\multicolumn{2}{|r|}{Time-slice TN} & 
		\multicolumn{2}{c|}{ 592 }  \\
		\hline \hline

		\multicolumn{2}{|r|}{Time-slice sensitivity} & 
		\multicolumn{2}{c|}{ 0.929292929 } &
		\multicolumn{2}{|r|}{Sensitivity} & 
		\multicolumn{2}{c|}{ 1 } \\

		\multicolumn{2}{|r|}{Time-slice specificity} & 
		\multicolumn{2}{c|}{ 0.996632997 } &
		\multicolumn{2}{|r|}{Specificity} & 
		\multicolumn{2}{c|}{ 1 } \\

		\multicolumn{2}{|r|}{Time-slice PPV} & 
		\multicolumn{2}{c|}{ 0.996389892 } &
		\multicolumn{2}{|r|}{PPV} & 
		\multicolumn{2}{c|}{ 1 } \\

		\multicolumn{2}{|r|}{Time-slice NPV} & 
		\multicolumn{2}{c|}{ 0.933753943 } &
		\multicolumn{2}{|r|}{NPV} & 
		\multicolumn{2}{c|}{ 1 } \\ \hline
	\end{tabular}
}
\label{table:tests_4}
\end{table}
\begin{figure}
\includegraphics[width=\linewidth]{images/tests_4}
\caption{Experiment 4. Accuracy and loss of network for training and validation data.}
\label{fig:tests_4}
\end{figure}

\begin{table}
\caption{Test results for experiment 5.}
\resizebox{\linewidth}{!}{%
	\begin{tabular}{ | c | c | c | c | c | c | c | c | }
		\hline
		patient & $Y_i$ & $N_{hc}$ & $N_p$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
		CTL15 & HC & 198 &   0   &  100  & 1 & HC & 100 \\
		CTL11 & HC & 198  &   0   &  100  & 1 & HC & 100 \\
		CTL07 & HC & 198 &   0   &  100  & 1 & HC & 100 \\
		ODP15 & P   &   0   & 198 &  100  & 0 &  P  & 100 \\
		ODP11 & P   &  34  &  164 &82.83& 0.1717 &  P  & 100 \\
		ODP07 & P  &   0   &  198 & 1 00  &0  &  P  & 100 \\ \hline
		\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 97.14 &
		\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 100 \\
		\hline \hline

		\multicolumn{2}{|r|}{True positive (TP)} & 
		\multicolumn{2}{c|}{ 3 } &
		\multicolumn{2}{|r|}{False positive (FP)} & 
		\multicolumn{2}{c|}{ 0 } \\ 
		\multicolumn{2}{|r|}{False negative (FN)} & 
		\multicolumn{2}{c|}{ 0 } &
		\multicolumn{2}{|r|}{True negative (TN)} & 
		\multicolumn{2}{c|}{ 3 }  \\
		\hline \hline

		\multicolumn{2}{|r|}{Time-slice TP} & 
		\multicolumn{2}{c|}{ 594 } &
		\multicolumn{2}{|r|}{Time-slice FP} & 
		\multicolumn{2}{c|}{ 34 } \\ 
		\multicolumn{2}{|r|}{Time-slice FN} & 
		\multicolumn{2}{c|}{ 0 } &
		\multicolumn{2}{|r|}{Time-slice TN} & 
		\multicolumn{2}{c|}{ 560 }  \\
		\hline \hline

		\multicolumn{2}{|r|}{Time-slice sensitivity} & 
		\multicolumn{2}{c|}{ 1 } &
		\multicolumn{2}{|r|}{Sensitivity} & 
		\multicolumn{2}{c|}{ 1 } \\

		\multicolumn{2}{|r|}{Time-slice specificity} & 
		\multicolumn{2}{c|}{ 0.942760943 } &
		\multicolumn{2}{|r|}{Specificity} & 
		\multicolumn{2}{c|}{ 1 } \\

		\multicolumn{2}{|r|}{Time-slice PPV} & 
		\multicolumn{2}{c|}{ 0.945859873 } &
		\multicolumn{2}{|r|}{PPV} & 
		\multicolumn{2}{c|}{ 1 } \\

		\multicolumn{2}{|r|}{Time-slice NPV} & 
		\multicolumn{2}{c|}{ 1 } &
		\multicolumn{2}{|r|}{NPV} & 
		\multicolumn{2}{c|}{ 1 } \\ \hline
	\end{tabular}
}
\label{table:tests_5}
\end{table}
\begin{figure}
\includegraphics[width=\linewidth]{images/tests_5}
\caption{Experiment 5. Accuracy and loss of network for training and validation data.}
\label{fig:tests_5}
\end{figure}

\begin{table}
\caption{Test results for experiment 6.}
\resizebox{\linewidth}{!}{%
	\begin{tabular}{ | c | c | c | c | c | c | c | c | }
		\hline
		patient & $Y_i$ & $N_{hc}$ & $N_p$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
		CTL10 & HC & 198 &  0 & 100 & 1 & HC & 100 \\
		CTL03 & HC & 198 &  0 & 100 & 1 & HC & 100 \\
		CTL02 & HC & 198 &  0 & 100 & 1 & HC & 100 \\
		ODP10 & P  &  0  & 198 & 100 & 0 &  P  & 100 \\
		ODP03 & P  &  0  & 198 & 100 & 0 &  P  & 100 \\
		ODP02 & P  &  0  & 198 & 100 & 0 &  P  & 100 \\ \hline
		\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 100 &
		\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 100 \\
		\hline \hline

		\multicolumn{2}{|r|}{True positive (TP)} & 
		\multicolumn{2}{c|}{ 3 } &
		\multicolumn{2}{|r|}{False positive (FP)} & 
		\multicolumn{2}{c|}{ 0 } \\ 
		\multicolumn{2}{|r|}{False negative (FN)} & 
		\multicolumn{2}{c|}{ 0 } &
		\multicolumn{2}{|r|}{True negative (TN)} & 
		\multicolumn{2}{c|}{ 3 }  \\
		\hline \hline

		\multicolumn{2}{|r|}{Time-slice TP} & 
		\multicolumn{2}{c|}{ 594 } &
		\multicolumn{2}{|r|}{Time-slice FP} & 
		\multicolumn{2}{c|}{ 0 } \\ 
		\multicolumn{2}{|r|}{Time-slice FN} & 
		\multicolumn{2}{c|}{ 0 } &
		\multicolumn{2}{|r|}{Time-slice TN} & 
		\multicolumn{2}{c|}{ 594 }  \\
		\hline \hline

		\multicolumn{2}{|r|}{Time-slice sensitivity} & 
		\multicolumn{2}{c|}{ 1 } &
		\multicolumn{2}{|r|}{Sensitivity} & 
		\multicolumn{2}{c|}{ 1 } \\

		\multicolumn{2}{|r|}{Time-slice specificity} & 
		\multicolumn{2}{c|}{ 1 } &
		\multicolumn{2}{|r|}{Specificity} & 
		\multicolumn{2}{c|}{ 1 } \\

		\multicolumn{2}{|r|}{Time-slice PPV} & 
		\multicolumn{2}{c|}{ 1 } &
		\multicolumn{2}{|r|}{PPV} & 
		\multicolumn{2}{c|}{ 1 } \\

		\multicolumn{2}{|r|}{Time-slice NPV} & 
		\multicolumn{2}{c|}{ 1 } &
		\multicolumn{2}{|r|}{NPV} & 
		\multicolumn{2}{c|}{ 1 } \\ \hline
	\end{tabular}
}
\label{table:tests_6}
\end{table}
\begin{figure}
\includegraphics[width=\linewidth]{images/tests_6}
\caption{Experiment 6. Accuracy and loss of network for training and validation data.}
\label{fig:tests_6}
\end{figure}

\begin{table}
\caption{Test results for experiment 7.}
\resizebox{\linewidth}{!}{%
	\begin{tabular}{ | c | c | c | c | c | c | c | c | }
		\hline
		patient & $Y_i$ & $N_{hc}$ & $N_p$ & $C_{i,t} (\%)$ & $P_i$ & $\hat{Y}_i$ & $C_i (\%)$ \\  \hline
		CTL05 & HC & 194 &  4   & 97.98 & 0.9798 & HC & 100 \\
		CTL04 & HC & 198 &  0   &   100  &      1     & HC & 100 \\
		CTL10 & HC & 186  &  12 & 93.94 & 0.9394 & HC & 100 \\
		ODP05 & P  &   0   & 198 &   100  &     0     &  P  & 100 \\
		ODP04 & P  &   0   & 198 &   100  &     0     &  P  & 100 \\
		ODP10 & P  &   0    & 198 &   100  &    0      &  P  & 100 \\ \hline
		\multicolumn{4}{|r|}{$\overline{C_{i,t}}$} & 98.65 &
		\multicolumn{2}{|r|}{$\overline{C_{i}}$} & 100 \\
		\hline \hline
